On mapping errors and seeding heuristics for DNA alignment

### 2019-04-08 MEM.tex
Ruggero on board
Removed myself from the acknowledgements.
Added myself in the authors list.
added a comment
On the role of the word "nearly" in section 1.2

\author[1,2]{Guillaume J. Filion}
\author[1,2]{Eduard Zorita}
\affil[1]{Genome Architecture, Gene Regulation, Stem Cells and Cancer
Programme, Center for Genomic Regulation (CRG), The Barcelona Institute of
Science and Technology, Dr. Aiguader 88, Barcelona 08003, Spain.}
\affil[2]{University Pompeu Fabra, Doctor Aiguader, 08003 Barcelona,
Spain.}

@@

This observation is fundamental: in order to estimate the error rate of of
a mapping algorithm, we must know how often the associated seeding
heuristic is off target. For lack of theoretical framework, this
information is missing for nearly all existing seeding methods, meaning
that current mappers cannot be properly calibrated.

@@

We thank Ruggero Cortini for suggesting Monte Carlo methods as a way to
tackle intractable cases. We acknowledge the financial support of the
Spanish Ministry of Economy and Competitiveness (‘Centro de Excelencia
Severo Ochoa 2013-2017’, Plan Nacional BFU2012-37168), of the CERCA
Programme~/~Generalitat de Catalunya, and of the European Research Council
(Synergy Grant 609989).

>>>>

\author[1,2]{Guillaume J. Filion}
\author[1,2]{Ruggero Cortini}
\author[1,2]{Eduard Zorita}
\affil[1]{Genome Architecture, Gene Regulation, Stem Cells and Cancer
Programme, Center for Genomic Regulation (CRG), The Barcelona Institute of
Science and Technology, Dr. Aiguader 88, Barcelona 08003, Spain.}
\affil[2]{University Pompeu Fabra, Doctor Aiguader, 08003 Barcelona,
Spain.}

@@

This observation is fundamental: in order to estimate the error rate of of
a mapping algorithm, we must know how often the associated seeding
heuristic is off target. For lack of theoretical framework, this
information is missing for nearly % nearly, or all? this is important because if
% there is at least one seeding algorithm that actually estimates correctly the
% probabilities for the seeding heuristics, then all of the rest is much less
% meaningful.
all existing seeding methods, meaning
that current mappers cannot be properly calibrated.

@@

We acknowledge the financial support of the Spanish Ministry of Economy and
Competitiveness (‘Centro de Excelencia Severo Ochoa 2013-2017’, Plan Nacional
BFU2012-37168), of the CERCA Programme~/~Generalitat de Catalunya, and of the
European Research Council (Synergy Grant 609989).
